\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{hyperref}
\usepackage{listings}
\usepackage{color}

% Example : https://codeforces.com/problemset/problem/266/A 
% So the title would be 266A - Stones on the Table
\title{158A - Next Round} 

% Author must be your full name
\author{Muhammad Arif Rifki} 

% Date is when you create this report
\date{17 April 2024}

\begin{document}

\maketitle

% There are 4 Sections, Problem, Objective, Solution, Code

% Problem section contains hyperlink to the problem
\section{Problem}

Problem Description : \href{https://codeforces.com/problemset/problem/158/A}{https://codeforces.com/problemset/problem/158/A}

% Objective section contains what is the problem's objective
\section{Objective}
"Contestant who earns a score equal to or greater than the k-th place finisher's score will advance to the next round, as long as the contestant earns a positive score..." — an excerpt from contest rules.

A total of n participants took part in the contest ($n \geq k$
), and you already know their scores. Calculate how many participants will advance to the next round.
\\\textbf{Input}

The first line of the input contains two integers n and k ($1 \leq k \leq n \leq 50$) separated by a single space.

The second line contains n space-separated integers $a_1, a_2, \ldots, a_n \quad (0 \leq a_i \leq 100)$
, where $ai$ is the score earned by the participant who got the i-th place. The given sequence is non-increasing (that is, for all i from 1 to $n-1$ the following condition is fulfilled: $a_i \geq a_{i+1}$).
\\\textbf{Output}

Output the number of participants who advance to the next round.
% Solution section contains how you approch the problem and your solution
\section{Solution}

To solve this question, we just need to create a variable to store the numbers in the k-1 array indices. then we use a loop to check each array number, whether the number in the array is more than 0, and more than or equal to the number in the array index k-1. we count it as the correct score.

% Code section contains your solution code

\newpage
\section{Code}

\lstset{language=C++,
        basicstyle=\ttfamily,
        keywordstyle=\color{blue}\ttfamily,
        stringstyle=\color{red}\ttfamily,
        commentstyle=\color{green}\ttfamily,
        morecomment=[l][\color{magenta}]{\#}
}
\begin{lstlisting}
#include <bits/stdc++.h>
using namespace std;
int main(){
    int a, b, cnt = 0;
    cin >> a >> b;
    int nums[a];
    for (int i = 0; i < a; i++){
        cin >> nums[i];
    }
    int core = nums[b - 1];
    for (int i = 0; i < a; i++){
        if (nums[i] > 0 && nums[i] >= core)
            cnt++;
    }
    cout << cnt;
    return 0;
}
\end{lstlisting}

\end{document}